Placeholder for article 3

### 2025-01-04 analysis/paper/paper.qmd
Retouch diversity tables

proto_retouch <- phase_dataset %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>%
  filter(Level %in% c("4E", "4E/5")) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  dplyr::group_by(RMTYPE)

proto_retouch_tab <- table(proto_retouch$RETOUCHEDPIECETYPOLOGY, proto_retouch$RMTYPE)
proto_retouch_tab <- as.data.frame.matrix(proto_retouch_tab)

>>>>

# Solutrean table
solu_retouch <- solutrean_dataset %>%
    mutate(CLASS = case_when(
    CLASS == "Retouched piece" ~ "RetouchedPiece",
    CLASS == "Retouched piece fragment" ~ "RetouchedPieceFrag",
    TRUE ~ CLASS)) %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  group_by(RMTYPE)

solu_retouch_tab <- solu_retouch %>% 
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>% 
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("col") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")

# Proto-solutrean table
proto_retouch <- phase_dataset %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>%
  filter(Level %in% c("4E", "4E/5")) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  dplyr::group_by(RMTYPE)

proto_retouch_tab <- proto_retouch %>%
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>%
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("col") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")

# Gravettian table
grav_retouch <- phase_dataset %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>%
  filter(Level %in% c(6, 7)) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  dplyr::group_by(RMTYPE)

grav_retouched_tab <- grav_retouch %>% 
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>%
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("col") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")
